\documentclass[12pt,letterpaper]{article}
\usepackage{fullpage}
\usepackage{url}
\makeatletter
\newcommand*{\textoverline}[1]{$\overline{\hbox{#1}}\m@th$}

\newcommand*{\fitb}[2]
{\raisebox{-1.3ex}{\textoverline{{\makebox[#1]{{\rule{0pt}{5pt}\tiny #2}}}}}}
\makeatother
\begin{document}
\raggedright
\centerline{\textbf{High-Speed Networking and Distributed Applications}}
\centerline{\textbf{Lab Exercise 1: Introduction to GENI and the GENI Portal}}
~\\
\centerline{\textbf{CS-491 \hfill Summer 2013}}
\noindent\rule{\textwidth}{1pt}

\bigskip
In this lab exercise, you will reserve some compute resources in the GENI 
environment using the graphical tool Flack. You will log into these virtual
machines and verify IP (layer 3) connectivity between them using 
\texttt{ping}. Time permitting, you will also disable IP connectivity between 
them and verify layer 2 connectivity using \texttt{pingPlus}.

\subsection*{Procedure}

\begin{description}

\item[Step 0:]
Obtain a GENI Portal account and join the CS491 project on the GENI Portal.

\item[Step 1:]
Generate and download your \texttt{ssh} keypair.

\item[Step 2:]
Create a slice in Flack with the name \fitb{1in}{username}\texttt{lab1}.

\item[Step 3:]
In Flack, reserve two virtual machines at the Kettering InstaGENI rack
(\texttt{geni.kettering.edu.cm}). Name one of them \texttt{client} and the 
other \texttt{server}.

Wait until the resources are ready (the Flack canvas will turn green).

\item[Step 4:]
Log into the nodes:

client login: \texttt{ssh -p}\fitb{0.5in}{port}\hspace{4pt}
\fitb{1in}{username}\texttt{@}\fitb{0.5in}{hostname}\texttt{.geni.kettering.edu}

server login: \texttt{ssh -p}\fitb{0.5in}{port}\hspace{4pt}
\fitb{1in}{username}\texttt{@}\fitb{0.5in}{hostname}\texttt{.geni.kettering.edu}

\item[Step 5:]
Verify IP (layer 3) connectivity between the two nodes by \texttt{ping}.

\texttt{server}'s data interface: \fitb{0.75in}{name} \fitb{2in}{IP address}

\texttt{client}'s data interface: \fitb{0.75in}{name} \fitb{2in}{IP address}

\item[\emph{Time permitting:}]
Disable IP connectivity and verify layer 2 connectivity between nodes 
by \texttt{pingPlus}.\\
\url{http://paws.kettering.edu/~chan7781/geni/pingPlus-0.2.tar.gz}

\texttt{server}'s data interface: \fitb{2in}{hardware address}

\item[Step 6:]
Clean up after yourself. Log out of your nodes, and delete your resources
or let them expire.

\end{description}

\subsection*{Acknowledgement}

Adapted from Edwards, S. \& Riga, N. (2013, July).
``Getting started with GENI and the GENI Portal, part 1''.
Presented at the \emph{17th GENI Engineering Conference}, Madison, Wisconsin.
\url{http://groups.geni.net/geni/wiki/GEC17Agenda/GettingStartedWithGENI_I}

\subsection*{Feedback?}
Questions? Comments? Concerns? Accolades? Insults? Send email to \url{chan7781@kettering.edu}.

\end{document}

